Selección de Instancias

### 2015-06-01 doc/paper.tex
Working on paper

\begin{table}[h]
\begin{tabular}{ |l|l|l|l|l| }
    \hline
     & LS & ILS & SA & TS  \\ \hline
    Glass & 22.6765 & 36.3244    & 32.0952 & 33.8730 \\ \hline
    Iris  & 6.2222 & 7.0018     & 8.0952  & 5.8966 \\ \hline
    Pima  & 43.6754 & 30.3922 & 32.6737       & 32.9629 \\ \hline
\end{tabular}
\caption{Resultados para tamaño de solución}
\label{tabla:2}
\end{table}

>>>>

\begin{table}[h]
\begin{tabular}{ |l|l|l|l|l| }
    \hline
     & LS & ILS & SA & TS  \\ \hline
    Glass & 40.6765 & 36.3244    & 32.0952 & 33.8730 \\ \hline
    Iris  & 6.2222 & 7.0018     & 8.0952  & 5.8966 \\ \hline
    Pima  & 43.6754 & 30.3922 & 32.6737       & 32.9629 \\ \hline
\end{tabular}
\caption{Resultados para tamaño de solución}
\label{tabla:2}
\end{table}
